Market simulator

### 2020-09-22 analysis/05_market_simulator.Rmd
Cleaning stuff up with Zack

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
)

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)
```

@@

  # Empty organization reactive table
  org_reactive <- as.data.frame(matrix(data, 24, 1))

  # Organization name inputs
  org_reactive[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
  # Expected utilities and market shares
  org_reactive[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
  # Persona name inputs
  org_reactive[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))

  # Rename columns
  colnames(org_reactive) <- c('Value', 'Organization', 'Type', 'Persona')

  ggplotly(
    org_reactive %>% 
      # Only care about the Market Share right now
      filter(Type == "Market Share") %>% 
      # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_id, input$per2_id, input$per3_id), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})
```

@@

# Issue area
selectInput(
  "org2_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

@@

# Issue area
selectInput(
  "org3_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

@@

# Issue area
selectInput(
  "org4_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

>>>>

# # Initial organization configuration
# organization_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
# )
# 
# # Initial persona configuration
# persona_data <- read_csv(
#   here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
# )
```

@@

  # Make data into a data frame
  plot_data <- as.data.frame(matrix(data, 24, 1))

  # Organization name inputs
  plot_data[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
  # Expected utilities and market shares
  plot_data[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
  # Persona name inputs
  plot_data[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))

  # Rename columns
  colnames(plot_data) <- c('Value', 'Organization', 'Type', 'Persona')

  ggplotly(
    plot_data %>% 
      # Only care about the Market Share right now
      filter(Type == "Market Share") %>% 
      # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_id, input$per2_id, input$per3_id), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})
```

@@

# Issue area
selectInput(
  "org2_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Environment",
  width = "450px"
)

@@

# Issue area
selectInput(
  "org3_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Human rights",
  width = "450px"
)

@@

# Issue area
selectInput(
  "org4_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Refugee relief",
  width = "450px"
)
